Pre-Project Review

### 2021-11-19 article/article.tex
Rough structure

\section{Introduction} \label{sec:Introduction}
Why millimetre waves?
Mention the meteorological radar range equation.
Brief mention of Rayleigh scattering.
The meteorological radar range equation, derived by Probert-Jones in 1962, is\supercite{ProbertJones}
\begin{equation}
	y = m x + c\label{eqn:MeteoRange}
\end{equation}

\section{Pulse Doppler radar} \label{sec:PulseDopperRadar}

\section{Continuous wave radar} \label{sec:CWR}

\section{Frequency-modulated continuous wave radar} \label{sec:FMCWR}

>>>>

\section{Introduction} \label{sec:Introduction}
Why millimetre waves?
Why is meteorological radar useful?

\section{Meteorological radar}
\subsection{Radar range equation}
Mention the radar range equation.
Brief mention of Rayleigh scattering.
The meteorological radar range equation, derived by Probert-Jones in 1962, is\supercite{ProbertJones}
\begin{equation}
	y = m x + c\label{eqn:MeteoRange}
\end{equation}

\section{Types of radar}
\subsection{Pulse Doppler radar} \label{sec:PulseDopperRadar}
Brief introduction to pulse Doppler radar.

\subsection{Continuous wave radar} \label{sec:CWR}
Introduction to continuous wave radar.

\subsection{Frequency-modulated continuous wave radar} \label{sec:FMCWR}
Continuous wave radar is useless without frequency modulation etc etc.
Why is this better than pulse Doppler radar?

\subsection{Solid state 94-GHz FMCW cloud profiling radar}
Discuss the radar at St. Andrews.

\subsubsection{Project work}
Discuss the rationale behind this project.
